The pollination trade-off

### 2018-11-11 paper/manuscript.Rmd
Add last paragraph intro

Elucidating competition for pollination at the community scale and the plants strategies to minimise it has been elusive is the sheer amount of data necessary to dissentangle them.

Perhaps the most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
Yet, evidence at the community scale of **the mutualistic trade-off**---the extent to which species degree affects the benefit---is scarce, to say the least. 
Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool might be involved.

Here, we explore the role that competition for pollinators plays on the quantity and quality of the pollination service and look for the signature of the mutualistic trade-off in diverse natural communities. 
To tease apart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that occur within it, all while accounting for the traits of the species that integrate the community.
Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
Second, we investigate whether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, functional originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context. 
Third, and finally, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.

>>>>

Here, we explore competiton for pollination at the community scale using comprehensive empirical data from eleven plant-pollinator communities in the Argentinean Pampas. 
First, we ask the extent to which the outcome of animal mediated pollination is facilitation or competition. 
If facilitation is the primary outcome we would expect (*i*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination and (*ii*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and that that would be achieved [@tur_evaluating_2016]. 
Second, we investigate the relative contribution that four ecological factors, that together, describe the role of the plant species and the ecological context, have on competition for pollination. 
We hypothesize that competition for pollination at the community level should increasse as the number of pollination partners a plant has increasses (species degree).
However, other factors like the plant's functional originality, its relative abbundance, and the visit effectiveness, should have the potential to compensate this increasse in competition by improving either the quality or the quality of pollination. 
Third, and finally, we explore how plants differ on how they use these factors to minimise competition. 
Although some plant species might be widespread across multiple locations, competition for pollinators ocurrs at the community level and are hence defined by the ecologica context. 
If plant species adopt comparable roles across different communities we should expect plant strategies to be more similar within species than across species in the study. 
On the contrary, if species role is flexible, we should expect plants to be able to adopt different strategies in each community such that competition is more optimaly minimised depending on the context.
